---
title: "BS_option"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BS_option}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
The BS_option function calculates the Black-Scholes option price, delta, and gamma for European call (CP = 'C') or put (CP = 'P') options based on specified parameters.

## Parameters

- `s`: Price of the underlying asset.
- `K`: Strike price of the option.
- `r`: Risk-free interest rate.
- `tau`: Time until maturity (in years).
- `sigma`: Implied volatility of the underlying asset.
- `CP`: Option type ('C' for call, 'P' for put).

## Usage
To use the BS_option function, provide the required parameters:
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CompStat.Package)
```

```{r}
# Calculate a European call option price, delta, and gamma
BS_option(100, 100, 0.02, 1, 0.2, 'C')
```

This will calculate the Black-Scholes option price, delta, and gamma for a European call option with the given parameters.

## Output
The function returns a list containing the calculated Black-Scholes option price, delta, and gamma based on the specified input parameters. These values provide insights into the option's pricing and sensitivity to changes in the underlying asset price.

In summary, the BS_option function offers a convenient tool for pricing and analyzing European call and put options using the Black-Scholes model.
